Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
wibbles

Our motivating enforcement mechanism,
the ``lazy'' stack safety micro-policies proposed by
Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}, permit functions
to write into one another's frames, but taint the result so that the frame's
owner cannot access it. No existing characterization of stack safety
captures this style of safety. We capture it by defining the properties in
terms of the observable behavior of the system.

@@

Two event traces $\obsT_1$ and $\obsT_2$ are {\em similar},
written \(\obsT_1 \eqsim \obsT_2\), if the sequence of non-silent events
is the same. That is, we compare up to deletion of \(\tau\) events.
Note that this results in an infinite silent trace being similar to
any trace. So, a trace that silently diverges due to a failstop will
fulfill this property vacuously.

@@

@@

The system we've modeled so far has been very simple, but our properties
support an important dimension of generality: adding features.\apt{Just what needs to be changed
to add these features?}
We now briefly introduce the features of our primary testing machine.\apt{Make sure
testing has been introduced properly before now. And why ``primary''?}

@@

Roessler and DeHon do not protect registers, but we consider registers to be
an extension of the stack. In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.
\apt{Presumably R\&dH don't care about registers because they already have
  the compiler in the TCB.  We should not (perhaps earlier than here!) that
  we have a stronger attacker model since we don't require the callee code
  to come from a trusted  compiler.}

>>>>

Our motivating enforcement mechanisms,
the ``lazy'' stack safety micro-policies proposed by
Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}, permit functions
to write into one another's frames, but taint the result so that the frame's
owner cannot access it. No existing characterization of stack safety
captures this style of safety. We capture it by defining the properties in
terms of the observable behavior of the system.

@@

Two event traces $\obsT_1$ and $\obsT_2$ are {\em similar},
written \(\obsT_1 \eqsim \obsT_2\), if the sequence of non-silent events
is the same. That is, we compare up to deletion of \(\tau\) events.
Note that this results in an infinite silent trace being similar to
any trace. So, a trace that silently diverges due to a failstop\apt{?? haven't explained this!}  will
fulfill this property vacuously.

@@

\apt{needs small transition}

@@

The system we model in \cref{sec:example,sec:formal} is very simple, but our properties
support an important dimension of generality: adding features.\apt{Just what needs to be changed
to add these features?}
We now briefly introduce the features of our primary testing machine.\apt{Make sure
testing has been introduced properly before now. And why ``primary''?}

@@

Roessler and DeHon do not protect registers, but we consider registers to be
an extension of the stack. In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.
\apt{Presumably R\&dH don't care about registers because they already have
  the compiler in the TCB.  We should note (perhaps earlier than here!) that
  we have a stronger attacker model since we don't require the callee code
  to come from a trusted  compiler.}
